### 2016-04-27 lineups.Rnw
done in purrr. figuring out how to extract estimates now

set.seed(12345)
ggplot(data = jTT, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='blue',vjust = -1, hjust =2, arrowgap = .05, colour = 'black') + 
  theme_net() + theme(legend.position = "none")
@

>>>>

set.seed(12345) # make shapes bigger, put labels in center. 
ggplot(data = jTT, aes(from_id = from, to_id = to)) + 
  geom_net(aes(shape = as.factor(group)), directed = T, label = T, labelcolour='blue',vjust = -1, hjust =2, arrowgap = .05, colour = 'black') + 
  theme_net() + theme(legend.position = "none")
@
